Exploring dimensions of biodiversity in Japanese ferns

### 2021-07-15 ms/SI.Rmd
Put Fig S7 in correct order in PDF
Don't write out separate files for SI figures

# Make iNEXT plot
inext_out$iNextEst %>%
  filter(method != "observed") %>%
  ggplot(aes(x=m, y=qD)) +
  geom_ribbon(aes(ymin = qD.LCL, ymax = qD.UCL), fill = "grey70") +
  geom_line(aes(linetype=method), size=0.8) +
  scale_linetype_manual(values=c("dotted", "solid", "solid")) +
  geom_point(data=observed_data, size=3) +
  scale_y_continuous("Richness") +
  scale_x_continuous("No. specimens") +
  theme_minimal() +
  theme(
    legend.position="bottom", 
    legend.title=element_blank()
  )

ggsave(result_file(s_figure("sampling-curve"), "pdf"), width = 4, height = 3, units = "in")
```

@@

a + b + c +
  plot_annotation(tag_levels = 'A')

ggsave(result_file(s_figure("grain-size"), "pdf"), width = 7, height = 3, units = "in")
```

@@

a + b + c + d + e + f + plot_layout(ncol = 2, nrow = 3)

ggsave(result_file(figure("envir"), "pdf"), width = 6, height = 8, units = "in")
```

@@

a + b + 
  plot_layout(nrow = 1)

ggsave(result_file(figure("abundance"), "pdf"), width = 7, height = 5, units = "in")
```

@@

a + b +
  plot_layout(ncol = 2) +
  plot_annotation(tag_levels = 'A')

ggsave(result_file(s_figure("k-plot"), "pdf"), width = 7, height = 3, units = "in")
```

@@

a + b + c + d +
  plot_layout(ncol = 2, nrow = 2) +
  plot_annotation(tag_levels = 'A')

ggsave(result_file(s_figure("raw-biplot"), "pdf"), width = 7, height = 3, units = "in")
```

@@

```{r endemism-restricted, fig.width = 5, fig.height = 5}
ggplot() +
  geom_sf(data = japan, fill = "grey90", color = "black", lwd = 0.25) +
  geom_sf(data = biodiv_ferns_endemic_spatial, aes(fill = endem_type), color = "transparent", alpha = 0.8) +
  scale_fill_manual(values = canape_cols) +
  map_theme() +
  theme(legend.title = element_blank())

ggsave(result_file(s_figure("endemism-restricted"), "pdf"), width = 5, height = 5, units = "in")
```

@@

>>>>

# Make iNEXT plot
inext_out$iNextEst %>%
  filter(method != "observed") %>%
  ggplot(aes(x=m, y=qD)) +
  geom_ribbon(aes(ymin = qD.LCL, ymax = qD.UCL), fill = "grey70") +
  geom_line(aes(linetype=method), size=0.8) +
  scale_linetype_manual(values=c("dotted", "solid", "solid")) +
  geom_point(data=observed_data, size=3) +
  scale_y_continuous("Richness") +
  scale_x_continuous("No. specimens") +
  theme_minimal() +
  theme(
    legend.position="bottom", 
    legend.title=element_blank()
  )
```

@@

a + b + c +
  plot_annotation(tag_levels = 'A')
```

@@

a + b + c + d + e + f + plot_layout(ncol = 2, nrow = 3)
```

@@

a + b + 
  plot_layout(nrow = 1)
```

@@

@@

a + b + c + d +
  plot_layout(ncol = 2, nrow = 2) +
  plot_annotation(tag_levels = 'A')
```

@@

```{r endemism-restricted, fig.width = 5, fig.height = 5}
ggplot() +
  geom_sf(data = japan, fill = "grey90", color = "black", lwd = 0.25) +
  geom_sf(data = biodiv_ferns_endemic_spatial, aes(fill = endem_type), color = "transparent", alpha = 0.8) +
  scale_fill_manual(values = canape_cols) +
  map_theme() +
  theme(legend.title = element_blank())
```

@@

a + b +
  plot_layout(ncol = 2) +
  plot_annotation(tag_levels = 'A')
```
